---
title       : Predicting Stock Price
subtitle    : Yes it's true Stock Price can be predicted
author      : Data Product Student
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---
## New App to predict stock price

### This App predicts stock price based on trading volume
### Uses Linear Programming model 
### Model is trained with historical data 
### Model is verified to be working with test data
### Free test version available
http://maheshwaria.shinyapps.io/stockPrediction

---

## Building  model on training data

```{r}
pTr<-c(80.75,200.75,90.75,60.75,22.75,150.75,350.75,13.25,36.25,42.25,80.75,200.75,90.75,
     60.75,22.75,150.75,350.75,13.25,36.25,42.25,80.75,200.75,90.75,60.75,22.75,150.75,
     350.75,13.25,36.25,42.25)
vTr<-c(160,401,180,120,44,300,700,25,71,83,161,400,180,120,44,300,700,25,71,83,160,400,
     180,120,44,301,701,25,71,83)
fit<-lm(pTr~vTr)
fit
```

---
## Review the model
```{r}
plot(vTr,pTr,pch=24,col="red",xlab="Trading Volume",ylab="Stock Price")
lines(vTr,fit$fitted,lwd=3)
```

--- 

## Lets Predict

```{r}
pTest<-c(88.29,43.9,46.3,351,451); vTest<-c(175,86,91,700,900)
round(predict(fit,data.frame(vTr=vTest)),2)
```
### Lets compare training and test set errors 
```{r}
sqrt(sum((fit$fitted-pTr)^2)); sqrt(sum((predict(fit,data.frame(vTr=vTest))-pTest)^2))

```

### (Our model worked better on test data.)





